Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-09-09 ms.tex
nearly finished all changes from referee.

We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
The ThAr data is taken for wavelength calibration with the 0.3$\arcsec\times60\arcsec$ slit since it has a resolving power high enough to separate the ThAr lines and identify them.
This wavelength calibration data is taken at the very beginning and very end of the sequence to ensure the 3$\arcsec \times 60 \arcsec$ slit is unmoved during the rest of the calibration and science data.
Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
We \textbf{took} flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum. 
To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
These shifts were used to apply a custom flat field for every image\textbf{, while shifting the sky flat (with pixel-to-pixel response removed) and maintaining the position of the pixel-to-pixel flat}.
For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.

@@

Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserDetrend}.
The baseline trends (which scale linearly with time and linearly with airmass) have been removed from Figure~\ref{fig:tserDetrend}, but the original light curves can be viewed in Figure \ref{fig:tserNoDetrend}.
The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period for each brown dwarf and compare it to the expected photon and read noise.
In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.

@@

Each of the raw light curves were fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is the period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
We impose 2.6 $< \tau <$ 3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
We do not put any constraints on A$_1$ relative to A$_2$.
The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.

@@

We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral types L4-L5: {\sha} and {\shb}.
These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
We find that {\sha} has marginal variability and no significant wavelength dependence; while
{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m), which declines toward the near infrared (2.4$~\mu$m).
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.

>>>>

We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
The ThAr data is taken for wavelength calibration with the 0.3$\arcsec\times60\arcsec$ slit since it has a resolving power high enough to separate the ThAr lines and identify them.
This wavelength calibration data is taken at the very beginning and very end of the sequence to ensure the 3$\arcsec \times 60 \arcsec$ slit is unmoved during the rest of the calibration and science data.
Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
We \textbf{took} flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum. 
To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
These shifts were used to apply a custom flat field for every image\textbf{: the illumination flat (with pixel-to-pixel flat removed) is shifted to the cross correlation peaks and multiplied by the pixel-to-pixel flat structure, which is maintained at the same position}.
For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.

@@

Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserDetrend}.
The baseline trends (which scale linearly with time and linearly with airmass) have been removed from Figure~\ref{fig:tserDetrend}, but the original light curves can be viewed in Figure \ref{fig:tserNoDetrend}.
The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
We measure the standard deviation of the time series for wavelength regions that have no significant variations near the rotation period for each brown dwarf and compare it to the expected photon and read noise.
In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.

@@

Each of the raw light curves \textbf{was} fit to a double sinusoidal model:
\begin{equation}\label{eq:cosfit}
\begin{split}
F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
\times (B t + C + D a(t))
\end{split}
\end{equation}
where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is the period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
We impose 2.6 $< \tau <$ 3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
We do not put any constraints on A$_1$ relative to A$_2$.
The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.

@@

We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral types L4-L5: {\sha} and {\shb}.
These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
We find that {\sha} has marginal variability and no significant wavelength dependence; while
{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m), which declines toward the near infrared (2.4$~\mu$m).
A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
\sha\ shows less variability \textbf{than reported in the literature} \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.
